---
title: "viralMIBI-postannotation_cleanup figures"
author: "Sizun Jiang"
date: "15/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(echo = TRUE) 
knitr::opts_knit$set(root.dir = "/Users/sizunj/Nolan Lab Dropbox/Sizun Jiang/projects/DNAscope/Data/MIBI/DNAscope Manuscript Data/ConvertedToPoints/Analysis/viralMIBI/")

# setwd("/Users/sizunj/Nolan Lab Dropbox/Sizun Jiang/projects/DNAscope/Data/MIBI/NewTissuesSlides97-101/Tiled Data 3 Depths/Analysis")
```

## R Markdown

```{r, echo=FALSE, warning=FALSE, error=FALSE}
library(FNN)
library(flowCore)
library(R.matlab)
library(FlowSOM)
library(MetaCyto)
library(matrixStats)
library(ggplot2)
library(reshape2)
library(dplyr)
library(limma)
library(ggrepel)
library(RColorBrewer)
library(pheatmap)
library(ConsensusClusterPlus)
library(Biobase)
library(MEM)
library(tidyverse)
library(Rtsne)
library(uwot)
library(ComplexHeatmap)
library(bioimagetools)
library(magick)
library(EBImage)
library(jamba)
library(patchwork)
library(preprocessCore)
library(gplots)
library(spatstat)
library("ggpubr")
library(PCAtools)
library(tidyverse)

source("/Users/sizunj/Nolan Lab Dropbox/Sizun Jiang/projects/MIBI/functions/MIBI_functions.R")
library(randomForest)
library(ROCR)
library(matrixStats)
source("/Users/sizunj/Nolan Lab Dropbox/Sizun Jiang/projects/MIBI/functions/random forest functions.R")
library(caret)

expr2_df_cent = read.csv("22Feb21_CN2df_newactivecells.csv")
```



```{r, fig.height=8, fig.width=16}

mycolor_celltype =c(brewer.pal(n = 9, name = "Set1"),brewer.pal(n = 8, name = "Pastel2"))
mycolor_celltype = replace(mycolor_celltype, c(2, 1), mycolor_celltype[c(1, 2)])
mycolor_celltype = replace(mycolor_celltype, c(2, 3), mycolor_celltype[c(3, 2)])

mycolor_celltype = mycolor_celltype[-c(9,10)]
mycolor_celltype = replace(mycolor_celltype, c(12, 15), mycolor_celltype[c(15, 12)])
celltype_table = table(expr2_df_cent$cell_type)

ggdf_Point2 = data.frame(sample_id = factor(names(celltype_table), levels = names(celltype_table)[mixedOrder(names(celltype_table))]),

g2 = ggplot(ggdf_Point2, aes(x = as.factor(sample_id), y = counts, fill = sample_id))
g2 + geom_bar(stat = "identity") + scale_fill_manual(values = mycolor_celltype) +
geom_text(aes(label = counts), hjust=0.5, vjust=-0.5, size = 4) + theme_bw() +ggtitle("Cell Type Statistics") + xlab("Cluster") 


```
Marker Expression Profile
```{r, fig.width=4, fig.height=4}
cell_type_label = expr2_df_cent$cell_type

require(gplots)
mat_markers = expr2_df_cent[,c(10, 12:41)]
  mat_cor = cor(mat_markers,method="pearson")
  
  colors = c(seq(0,1,length=22))
  my_palette <- rev(colorRampPalette(brewer.pal(6,"RdBu"))(n = 21))
  
  hm2_call = heatmap.2(mat_cor,col=my_palette,breaks=colors,density.info="none",trace="none",Rowv=T,Colv=T,dendrogram="both",symm=T,labRow=colnames(mat_markers),labCol=colnames(mat_markers),margins=c(5,5),scale="none",cexRow=0.8,cexCol=0.8,rowsep=c(0:50),colsep=c(0:50),sepcolor="black",sepwidth=c(0.0001,0.0001))
  # New color
  require(pals)
  require(svglite)
  colors = c(seq(-3,3,length=100))
  my_palette <- coolwarm(99)
  
  # Save as SVG
  svglite(file = "PaperPlots/CellTypeHeatmap.svg",
      width = 10,
      height = 10
      # system_fonts = list(sans = "Arial Unicode MS")
      # dpi = 300
      )
  
  hm2_call = heatmap.2(cell_type_mat,col=my_palette,breaks=colors,density.info="none",trace="none",Rowv=F,Colv=F,dendrogram="none",symm=F,labRow=cell_types,labCol=colnames(mat_markers),
                       margins=c(6*(dim(cell_type_mat)[2]/dim(cell_type_mat)[1]),6),
                       scale="col",cexRow=1,cexCol=1,rowsep=c(0:20),colsep=c(0:33),sepcolor="black",sepwidth=c(0.0001,0.0001))

  dev.off()
```


CN color scheme
```{r}
CN_colors =c(brewer.pal(n = 8, name = "Dark2"), brewer.pal(n = 9, name = "Pastel1"))
CN_colors = CN_colors[-c(5,7)]
CN_colors = replace(CN_colors, c(4, 10), CN_colors[c(10, 4)])

```

Plot per FOV etc. First lets do all the plots without relationship to CNs (cos "Others" taken out in CNs)
```{r}
plot_df = cbind(expr2_df_cent[,c("PointNum", "PointName", "Animal", "Infected", "cell_type", "SIV_Status")])
plot_df = plot_df[!plot_df$cell_type %in% "Other",]

# Get levels right
names(mycolor_celltype) = levels(expr2_df_cent$cell_type)

# Ordering things so that order for pointnum and animal are SIV+ then SIV-
plot_df$PointNum = factor(plot_df$PointNum, levels = c(1:6, 14:20, 7:13))
plot_df$Animal = factor(plot_df$Animal, levels = c(1,2,5,6,3,4))
plot_df$Infected[plot_df$Infected == 0] = "Uninfected Animal"
plot_df$Infected[plot_df$Infected == 1] = "Infected Animal"
plot_df$Infected = factor(plot_df$Infected, levels = c("Infected Animal", "Uninfected Animal"))

# By Point Num
ggplot(plot_df,aes(x=PointNum,fill=cell_type)) + geom_bar(position="fill") +  scale_fill_manual(values=mycolor_celltype[names(mycolor_celltype) %in% plot_df$cell_type]) +
  labs(x = "Field of View", y = "Proportion",title = "Cell Type Composition per Field of View") + theme_bw()  + labs(fill = "Cell Type")
ggsave("PaperPlots/CellType_perFOV.svg")
# By Point Name
ggplot(plot_df,aes(x=Animal,fill=cell_type)) + geom_bar(position="fill") +  scale_fill_manual(values=mycolor_celltype[names(mycolor_celltype) %in% plot_df$cell_type]) +
  labs(x = "Animal", y = "Proportion",title = "Cell Type Composition per Animal") + theme_bw()   + labs(fill = "Cell Type")
ggsave("PaperPlots/CellType_perAnimal.svg")

ggplot(plot_df,aes(x=Infected,fill=cell_type)) + geom_bar(position="fill") +  scale_fill_manual(values=mycolor_celltype[names(mycolor_celltype) %in% plot_df$cell_type]) +
  labs(x = "Animal Infection Status", y = "Proportion",title = "Cell Type Composition per Animal Infection Status") + theme_bw()  + labs(fill = "Cell Type")
ggsave("PaperPlots/CellType_perInfectionStatus.svg")

```
Plot FoldChange of each celltype over uninfected
```{r}
uninf_celltype_tab = prop.table(table(plot_df$cell_type[plot_df$Infected %in% "Uninfected Animal"]))
inf_celltype_tab = prop.table(table(plot_df$cell_type[plot_df$Infected %in% "Infected Animal"]))
df = as.data.frame(log2(inf_celltype_tab/uninf_celltype_tab))
# Rank celltypes
df$Var1 = factor(df$Var1, levels = df$Var1[order(df$Freq, decreasing = T)])



ggplot(df, aes(x = Var1, y = Freq, fill = Var1)) + geom_bar(stat = "identity", color = "black") +  scale_fill_manual(values=mycolor_celltype[order(df$Freq, decreasing = T)]) +
  labs(x = "Cell Types", y = "Log2 Fold Enrichment",title = "Log2 FC Cell Type Composition of Infected/Uninfected Rhesus Macaques") + theme_bw()  + labs(fill = "Cell Type")+ theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))

ggsave("PaperPlots/CellType_Log2FC_perInfectionStatus.svg")

```

Rank by % per FOV of: 
1: CD8
2: Macrophage
3: Infected Cell
```{r}
# First on FOVs
infiltrate_df = do.call(rbind, lapply(1:20, function(fov){
  sub_df = plot_df$cell_type[plot_df$PointNum %in% fov]
  sub_df_out = as.data.frame(prop.table(table(sub_df))*100)
  sub_df_out$PointNum = fov
  sub_df_out$Infected = unique(plot_df$Infected[plot_df$PointNum %in% fov])
  colnames(sub_df_out)[1] = "cell_type"
  return(sub_df_out)
}))

rank_plots = lapply(unique(infiltrate_df$cell_type), function(ct){
  sub_df = infiltrate_df[infiltrate_df$cell_type %in% ct,]
  p = ggplot(sub_df, aes(x = reorder(PointNum,Freq), y = Freq, fill = Infected)) + geom_bar(stat = "identity", color = "black") + labs(x = "FOVs", y = "Percent Infiltrating",title = paste0("Ranked Infiltration of: ", ct)) + theme_bw()  + labs(fill = "Cell Type")+ coord_flip()
  ggsave(plot = p, filename = paste0("viralMIBI/PaperPlots/CellType_Ranking_", ct,".svg"))
  return(p)
})

lapply(rank_plots, function(p){
  p
})

# SIV_status_tab = do.call(rbind, lapply(1:20, function(fov){
#   sub_df = plot_df[plot_df$PointNum %in% fov,]
#   sub_df_out = as.data.frame(prop.table(table(sub_df$SIV_Status))*100)
#   sub_df_out$PointNum = fov
#   return(sub_df_out)
# }))
# 
#  = prop.table(table(plot_df$SIV_Status[plot_df$Infected %in% "Infected Animal"]))
# 

```


Clean up CN2 csv to have additional info


```{r}
plot_df2 = cbind(expr2_df_cent[,c("PointNum", "Animal", "Infected", "cell_type", "SIV_Status", "neighborhood20")])

# Ordering things so that order for pointnum and animal are SIV+ then SIV-
plot_df2$PointNum = factor(plot_df2$PointNum, levels = c(1:6, 14:20, 7:13))
plot_df2$Animal = factor(plot_df2$Animal, levels = c(1,2,5,6,3,4))
plot_df2$Infected[plot_df2$Infected == 0] = "Uninfected Animal"
plot_df2$Infected[plot_df2$Infected == 1] = "Infected Animal"
plot_df2$Infected = factor(plot_df2$Infected, levels = c("Infected Animal", "Uninfected Animal"))
plot_df2$neighborhood20 = as.factor(plot_df2$neighborhood20)

# By Point Num
ggplot(plot_df2,aes(x=PointNum,fill=neighborhood20)) + geom_bar(position="fill") +  scale_fill_manual(values=CN_colors) +
  labs(x = "Field of View", y = "Proportion",title = "Cell Type Composition per Field of View") + theme_bw()  + labs(fill = "Cell Neighborhood")
ggsave("PaperPlots/CN_perFOV.svg")
# By Point Name
ggplot(plot_df2,aes(x=Animal,fill=neighborhood20)) + geom_bar(position="fill") +  scale_fill_manual(values=CN_colors) +
  labs(x = "Animal", y = "Proportion",title = "Cell Type Composition per Animal") + theme_bw()   + labs(fill = "Cell Neighborhood")
ggsave("PaperPlots/CN_perAnimal.svg")

ggplot(plot_df2,aes(x=Infected,fill=neighborhood20)) + geom_bar(position="fill") +  scale_fill_manual(values=CN_colors) +
  labs(x = "Animal Infection Status", y = "Proportion",title = "Cell Type Composition per Animal Infection Status") + theme_bw()  + labs(fill = "Cell Neighborhood")
ggsave("PaperPlots/CN_perInfectionStatus.svg")

```

Plot FoldChange of each CN over uninfected
```{r}
uninf_CN_tab = prop.table(table(plot_df2$neighborhood20[plot_df2$Infected %in% "Uninfected Animal"]))
inf_CN_tab = prop.table(table(plot_df2$neighborhood20[plot_df2$Infected %in% "Infected Animal"]))
df2 = as.data.frame(log2(inf_CN_tab/uninf_CN_tab))

# Order df3 by frequency
df2$Var1 = factor(df2$Var1, levels = df2$Var1[order(df2$Freq, decreasing = T)])

ggplot(df2, aes(x = Var1, y = Freq, fill = Var1)) + geom_bar(stat = "identity", color = "black") +  scale_fill_manual(values=CN_colors[order(df2$Freq, decreasing = T)]) +
  labs(x = "CNs", y = "Log2 Fold Enrichment",title = "Log2 FC Cell Type Composition of Infected/Uninfected Rhesus Macaques") + theme_bw()  + labs(fill = "Cell Neighborhoods")+ theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))
ggsave("PaperPlots/CN_Log2FC_perInfectionStatus.svg")

```
Rank plots for CNs per FOV
```{r}
# First on FOVs
infiltrate_df2 = do.call(rbind, lapply(1:20, function(fov){
  sub_df = plot_df2$neighborhood20[plot_df2$PointNum %in% fov]
  sub_df_out = as.data.frame(prop.table(table(sub_df))*100)
  sub_df_out$PointNum = fov
  sub_df_out$Infected = unique(plot_df2$Infected[plot_df2$PointNum %in% fov])
  colnames(sub_df_out)[1] = "CNs"
  return(sub_df_out)
}))

CN_nam = c("T/DC/NK Rich",
           "B Cell Zone",
           "Macrophage Rich 2",
           "T Cell Zone",
           "B/NK/Monocyte Rich",
           "CD4 T Cell Rich",
           "FDC Rich",
           "Macrophage Rich 1",
           "Stromal/Endothelial",
           "CD8 T Cell Infiltrate",
           "Immune Infiltrate")

rank_plots2 = lapply(unique(infiltrate_df2$CNs), function(ct){
  sub_df = infiltrate_df2[infiltrate_df2$CNs %in% ct,]
  p = ggplot(sub_df, aes(x = reorder(PointNum,Freq), y = Freq, fill = Infected)) + geom_bar(stat = "identity", color = "black") + labs(x = "FOVs", y = "Percent Infiltrating",title = paste0("Ranked Infiltration of: ", CN_nam[as.numeric(ct)])) + theme_bw()  + labs(fill = "CNs")+ coord_flip()
  ggsave(plot = p, filename = paste0("PaperPlots/CN_Ranking_", ct,".svg"))
  return(p)
})

lapply(rank_plots2, function(p){
  p
})

```


## CN diff for each marker between SIV+ and SIV-
Each dot should be 1 FOV
Include Stats Test

```{r, fig.width=12, fig.height=5}
# require(tidyverse)
library(reshape2)
sub_df = cbind(expr2_df_cent[,c(12,14:43)], expr2_df_cent[,c("Groups", "PointNum", "neighborhood20text")])
sub_df2 = data.frame(sub_df %>% group_by(PointNum, neighborhood20text) %>%
  summarise(across(Vimentin:Groups, mean)))
plot_CN_withmarkers = melt(sub_df2,
                           id.vars = c("Groups", "neighborhood20text", "PointNum"),
                           variable.name = "Marker")
plot_CN_withmarkers$Groups[plot_CN_withmarkers$Groups == 0] = "Uninfected Animal"
plot_CN_withmarkers$Groups[plot_CN_withmarkers$Groups == 1] = "Infected Animal"
plot_CN_withmarkers$Groups = factor(plot_CN_withmarkers$Groups, levels = c("Infected Animal", "Uninfected Animal"))
colnames(plot_CN_withmarkers)[colnames(plot_CN_withmarkers) %in% "neighborhood20text"] = "CN"

colnames(plot_CN_withmarkers)[colnames(plot_CN_withmarkers) %in% "variable"] = "Marker"
# Find average expression per FOV

CN_marker_diff = lapply(unique(expr2_df_cent$neighborhood20text), function(cn){
  sub_plotdf = plot_CN_withmarkers[plot_CN_withmarkers$CN %in% cn,]
  p = ggplot(data=sub_plotdf, aes(x=Marker, y=value, fill=Groups)) + geom_boxplot(outlier.shape = NA) +
    # geom_jitter(color="black", size=0.1, alpha=1, width = 0.05, height = 0.05) +
    geom_point(position=position_jitterdodge(), size = 0.5)+
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  compare_means(value ~ Groups, data = sub_plotdf,
                group.by = "Marker")
  g = p + stat_compare_means(label = "p.signif", size = 5) + ggtitle(paste0("Enrichment in CN ", cn)) + theme_bw() + ylab("Expression") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

  ggsave(plot = g, filename = paste0("PaperPlots/CN_Marker_Enrichment_", cn,".svg"), width = 12, height = 6)
  return(g)
})

# lapply(CN_marker_diff, function(p){
#   p
# })
```
### Repeat for Cell Types
```{r, fig.width=12, fig.height=5}
sub_df = cbind(expr2_df_cent[,c(52:65)], expr2_df_cent[,c("Groups", "PointNum", "neighborhood20text")])
# sub_df = cbind(expr2_df_cent[,c(52:65)], expr2_df_cent[,c("Groups", "PointNum", "neighborhood20text")])

sub_df2 = sub_df %>% group_by(PointNum, neighborhood20text) %>%
  summarise(across(CD4_T:Groups, mean))
plot_CN_withmarkers = melt(sub_df2,
                           id.vars = c("Groups", "neighborhood20text", "PointNum"),
                           variable.name = "CellType")
plot_CN_withmarkers$Groups[plot_CN_withmarkers$Groups == 0] = "Uninfected Animal"
plot_CN_withmarkers$Groups[plot_CN_withmarkers$Groups == 1] = "Infected Animal"
plot_CN_withmarkers$Groups = factor(plot_CN_withmarkers$Groups, levels = c("Infected Animal", "Uninfected Animal"))
colnames(plot_CN_withmarkers)[colnames(plot_CN_withmarkers) %in% "neighborhood20text"] = "CN"

# Find average expression per FOV

CN_celltype_diff = lapply(unique(expr2_df_cent$neighborhood20text), function(cn){
  sub_plotdf = plot_CN_withmarkers[plot_CN_withmarkers$CN %in% cn,]
  p = ggplot(data=sub_plotdf, aes(x=CellType, y=value, fill=Groups)) + geom_boxplot(outlier.shape = NA) +
    # geom_jitter(color="black", size=0.1, alpha=1, width = 0.05, height = 0.05) +
    geom_point(position=position_jitterdodge(), size = 0.5)+
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  compare_means(value ~ Groups, data = sub_plotdf,
                group.by = "CellType")
  g = p + stat_compare_means(label = "p.signif", size = 5) + ggtitle(paste0("Enrichment in CN ", cn)) + theme_bw() + ylab("Expression") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

  ggsave(plot = g, filename = paste0("PaperPlots/CN_CellType_Enrichment2_", cn,".svg"), width = 12, height = 6)
  return(g)
})

```
Write a function to do the comparisons for the above:
1. Per Marker
2. Expression across CNs in +/- SIV

```{r, fig.width=12, fig.height=5}
# Recalculate this chuck since chuck before used CellTypes vs Markers
require(tidyverse)
require(reshape2)
sub_df = cbind(expr2_df_cent[,c(12,14:43)], expr2_df_cent[,c("Groups", "PointNum", "neighborhood20text")])
sub_df2 = sub_df %>% group_by(PointNum, neighborhood20text) %>%
  summarise(across(Vimentin:Groups, mean))
plot_CN_withmarkers = melt(sub_df2,
                           id.vars = c("Groups", "neighborhood20text", "PointNum"),
                           variable.name = "Marker")
plot_CN_withmarkers$Groups[plot_CN_withmarkers$Groups == 0] = "Uninfected Animal"
plot_CN_withmarkers$Groups[plot_CN_withmarkers$Groups == 1] = "Infected Animal"
plot_CN_withmarkers$Groups = factor(plot_CN_withmarkers$Groups, levels = c("Infected Animal", "Uninfected Animal"))
colnames(plot_CN_withmarkers)[colnames(plot_CN_withmarkers) %in% "neighborhood20text"] = "CN"

# Find average expression per FOV

CN_marker_diff2 = lapply(unique(plot_CN_withmarkers$Marker), function(marker){
  sub_plotdf = plot_CN_withmarkers[plot_CN_withmarkers$Marker %in% marker,]
  p = ggplot(data=sub_plotdf, aes(x=CN, y=value, fill=Groups)) + geom_boxplot(outlier.shape = NA) +
    # geom_jitter(color="black", size=0.1, alpha=1, width = 0.05, height = 0.05) +
    geom_point(position=position_jitterdodge(), size = 0.5)+
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  compare_means(value ~ Groups, data = sub_plotdf,
                group.by = "CN")
  g = p + stat_compare_means(label = "p.signif", size = 5) + ggtitle(paste0("Enrichment for Marker: ", marker)) + theme_bw() + ylab("Expression") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

  ggsave(plot = g, filename = paste0("viralMIBI/PaperPlots/CN_Marker_Enrichment_permarker_", marker,".svg"), width = 12, height = 6)
  return(g)
})
```

1. Per CellType
2. Enrichment/Number across CNs in +/- SIV
```{r, fig.width=12, fig.height=5}
# Recalculate this chuck since chuck before used CellTypes vs Markers
require(tidyverse)
require(reshape2)
sub_df = cbind(expr2_df_cent[,c(52:65)], expr2_df_cent[,c("Groups", "PointNum", "neighborhood20text")])
sub_df2 = sub_df %>% group_by(PointNum, neighborhood20text) %>%
  summarise(across(B:Groups, mean))
plot_CN_withmarkers = melt(sub_df2,
                           id.vars = c("Groups", "neighborhood20text", "PointNum"),
                           variable.name = "CellType")
plot_CN_withmarkers$Groups[plot_CN_withmarkers$Groups == 0] = "Uninfected Animal"
plot_CN_withmarkers$Groups[plot_CN_withmarkers$Groups == 1] = "Infected Animal"
plot_CN_withmarkers$Groups = factor(plot_CN_withmarkers$Groups, levels = c("Infected Animal", "Uninfected Animal"))
colnames(plot_CN_withmarkers)[colnames(plot_CN_withmarkers) %in% "neighborhood20text"] = "CN"

# Find average expression per FOV

CN_celltype_diff2 = lapply(unique(plot_CN_withmarkers$CellType), function(celltype){
  sub_plotdf = plot_CN_withmarkers[plot_CN_withmarkers$CellType %in% celltype,]
  p = ggplot(data=sub_plotdf, aes(x=CN, y=value, fill=Groups)) + geom_boxplot(outlier.shape = NA) +
    # geom_jitter(color="black", size=0.1, alpha=1, width = 0.05, height = 0.05) +
    geom_point(position=position_jitterdodge(), size = 0.5)+
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  compare_means(value ~ Groups, data = sub_plotdf,
                group.by = "CN")
  g = p + stat_compare_means(label = "p.signif", size = 5) + ggtitle(paste0("Enrichment for CellType: ", celltype)) + theme_bw() + ylab("Expression") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

  ggsave(plot = g, filename = paste0("viralMIBI/PaperPlots/CN_Marker_Enrichment_perCellType_", celltype,".svg"), width = 12, height = 6)
  return(g)
})
```
## Fig 6 Paper Plot generation
```{r}
# subdf for cell types per CN
sub_df = cbind(expr2_df_cent[,c(12,14:43)], expr2_df_cent[,c("Groups", "PointNum", "neighborhood20text")])
sub_df2 = data.frame(sub_df %>% group_by(PointNum, neighborhood20text) %>%
  summarise(across(Vimentin:Groups, mean)))
plot_CN_withmarkers = melt(sub_df2,
                           id.vars = c("Groups", "neighborhood20text", "PointNum"),
                           variable.name = "Marker")
plot_CN_withmarkers$Groups[plot_CN_withmarkers$Groups == 0] = "Uninfected Animal"
plot_CN_withmarkers$Groups[plot_CN_withmarkers$Groups == 1] = "Infected Animal"
plot_CN_withmarkers$Groups = factor(plot_CN_withmarkers$Groups, levels = c("Infected Animal", "Uninfected Animal"))
colnames(plot_CN_withmarkers)[colnames(plot_CN_withmarkers) %in% "neighborhood20text"] = "CN"
colnames(plot_CN_withmarkers)[colnames(plot_CN_withmarkers) %in% "variable"] = "Marker"

# subdf for markers per CN
sub_df = cbind(expr2_df_cent[,c(52:65)], expr2_df_cent[,c("Groups", "PointNum", "neighborhood20text")])
sub_df2 = data.frame(sub_df %>% group_by(PointNum, neighborhood20text) %>%
  summarise(across(CD4_T:Groups, mean)))
plot_CN_withcelltype = melt(sub_df2,
                           id.vars = c("Groups", "neighborhood20text", "PointNum"),
                           variable.name = "CellType")
plot_CN_withcelltype$Groups[plot_CN_withcelltype$Groups == 0] = "Uninfected Animal"
plot_CN_withcelltype$Groups[plot_CN_withcelltype$Groups == 1] = "Infected Animal"
plot_CN_withcelltype$Groups = factor(plot_CN_withcelltype$Groups, levels = c("Infected Animal", "Uninfected Animal"))
colnames(plot_CN_withcelltype)[colnames(plot_CN_withcelltype) %in% "neighborhood20text"] = "CN"
colnames(plot_CN_withcelltype)[colnames(plot_CN_withcelltype) %in% "variable"] = "CellType"
```

```{r}
table(expr2_df_cent$neighborhood20text)
colnames(expr2_df_cent)
```

## Diff combinations for the paper
CN = "CD8_T_Cell_Infiltrate"
chosen_markers = c("Ki.67", "Granzyme.B", "NFkB.p100..pS865.")
chosen_celltypes = c("CD8_GzmB", "CD8_T")

CN = "FDC_Rich"
chosen_markers = c("Ki.67", "CD169..Sialoadhesin.", "NFkB.p100..pS865.", "CD138")
chosen_celltypes = c("Macrophage")

CN = "Immune_Infiltrate"
chosen_markers = c("Ki.67", "FoxP3", "Granzyme.B", "CD169..Sialoadhesin.", "NFkB.p100..pS865.", "IL10", "HLA-DR", "CD36", "FoxO1", "MPO")
chosen_celltypes = c("CD8_GzmB", "CD8_T", "Macrophage")

CN = "Macrophage_Rich_1"
chosen_markers = c("FoxO1", "IL10", "CD209..DC.SIGN.", "CD169..Sialoadhesin.")
chosen_celltypes = c("CD8_T")

CN = "Macrophage_Rich_2"
chosen_markers = c("FoxO1", "IL10", "CD209..DC.SIGN.", "CD169..Sialoadhesin.")
chosen_celltypes = c("CD8_T")

CN = "T_DC_NK_Rich"
chosen_markers = c("Ki.67", "NFkB.p100..pS865.", "IL10")
chosen_celltypes = c("DC", "NK", "CD8_T", "CD4_T") 

```{r}
CN = "Immune_Infiltrate"
chosen_markers = c("Ki.67", "FoxP3", "Granzyme.B", "CD169..Sialoadhesin.", "NFkB.p100..pS865.", "IL10", "HLA-DR", "CD36", "FoxO1", "MPO")
chosen_celltypes = c("CD8_GzmB", "CD8_T", "Macrophage")

sub_plotdf = plot_CN_withmarkers[plot_CN_withmarkers$Marker %in% chosen_markers,]
sub_plotdf = sub_plotdf[sub_plotdf$CN %in% CN,]
p = ggplot(data=sub_plotdf, aes(x=Marker, y=value, fill=Groups)) + geom_boxplot(outlier.shape = NA) +
  # geom_jitter(color="black", size=0.1, alpha=1, width = 0.05, height = 0.05) +
  geom_point(position=position_jitterdodge(), size = 0.5)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
compare_means(value ~ Groups, data = sub_plotdf,
              group.by = "CN")
p + stat_compare_means(label = "p.signif", size = 5) + ggtitle(paste0("Marker Enrichment for CN: ", CN)) + theme_bw() + ylab("Expression") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + ylim(c(0,0.3))

# ggsave(filename = paste0("viralMIBI/PaperPlots/Final_CN_Marker_Enrichment_", CN,".svg"), width = 12, height = 6)



sub_plotdf2 = plot_CN_withcelltype[plot_CN_withcelltype$CellType %in% chosen_celltypes,]
sub_plotdf2 = sub_plotdf2[sub_plotdf2$CN %in% CN,]

p = ggplot(data=sub_plotdf2, aes(x=CellType, y=value, fill=Groups)) + geom_boxplot(outlier.shape = NA) +
  # geom_jitter(color="black", size=0.1, alpha=1, width = 0.05, height = 0.05) +
  geom_point(position=position_jitterdodge(), size = 0.5)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
# compare_means(value ~ Groups, data = sub_plotdf2,
#               group.by = "CN")
p + stat_compare_means(label = "p.signif", size = 5) + ggtitle(paste0("Cell Type Enrichment for CN: ", CN)) + theme_bw() + ylab("Expression") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

ggsave(filename = paste0("PaperPlots/Final2_CN_CellType_Enrichment_", CN,".svg"), width = 12, height = 6)
  
```


```{r}
expr2_df_cent_mva = expr2_df_cent[,c(4,5, 67, 68, 66, 52:65, 70:100)]
expr2_df_cent_mva
# Summarize mean per CN
expr2_df_cent_mva = expr2_df_cent_mva %>% group_by(Groups, Patients, neighborhood20) %>%
  summarise(across(CD4_T:CD45_20_CN2, mean))
dim(expr2_df_cent_mva)
expr2_df_cent_mva
```

Profile Plot
```{r}
makeProfilePlot <- function(mylist,names)
  {
     require(RColorBrewer)
     # find out how many variables we want to include
     numvariables <- length(mylist)
     # choose 'numvariables' random colours
     colours <- brewer.pal(numvariables,"Set1")
     # find out the minimum and maximum values of the variables:
     mymin <- 1e+20
     mymax <- 1e-20
     for (i in 1:numvariables)
     {
        vectori <- mylist[[i]]
        mini <- min(vectori)
        maxi <- max(vectori)
        if (mini < mymin) { mymin <- mini }
        if (maxi > mymax) { mymax <- maxi }
     }
     # plot the variables
     for (i in 1:numvariables)
     {
        vectori <- mylist[[i]]
        namei <- names[i]
        colouri <- colours[i]
        if (i == 1) { plot(vectori,col=colouri,type="l",ylim=c(mymin,mymax)) }
        else         { points(vectori, col=colouri,type="l")                                     }
        lastxval <- length(vectori)
        lastyval <- vectori[length(vectori)]
        text((lastxval-10),(lastyval),namei,col="black",cex=0.6)
     }
  }

# library(RColorBrewer)
# names <- c("V2","V3","V4","V5","V6")
mylist <- as.list((expr2_df_cent_mva[,5:49]))
makeProfilePlot(mylist,colnames((expr2_df_cent_mva[,5:49])))
```
calculate summary statistics such as the mean and standard deviation for each of the variables in your multivariate data set.
```{r}
sapply(expr2_df_cent_mva[,4:48],mean)
sapply(expr2_df_cent_mva[,4:48],sd)
```
Standardizing Variables to Variance 1 and mean 0 using scale
Should not include vDNA or vRNA
```{r}
standardisedconcentrations <- as.data.frame(scale(expr2_df_cent_mva[,c(4:26,28:45, 47:48)]))
sapply(standardisedconcentrations,mean)
sapply(standardisedconcentrations,sd)
```

Try LDA. Note only using CN2 to avoid collinear
Impt: It doesn’t matter whether the input variables for linear discriminant analysis are standardised or not, unlike for principal components analysis in which it is often necessary to standardise the input variables. However, using standardised variables in linear discriminant analysis makes it easier to interpret the loadings in a linear discriminant function.

```{r, fig.width=5, fig.height=5}
require(MASS)
CN2.lda <- MASS::lda(standardisedconcentrations[,c(15:43)], grouping = expr2_df_cent_mva$Patients)
CN2.lda.values <- predict(CN2.lda, standardisedconcentrations[,c(15:43)])
# Proportion of trace is how much each % separation achieved by each LD
CN2.lda
ldahist(data = CN2.lda.values$x[,1], g=expr2_df_cent_mva$Patients)
ldahist(data = CN2.lda.values$x[,2], g=expr2_df_cent_mva$Patients)
ldahist(data = CN2.lda.values$x[,3], g=expr2_df_cent_mva$Patients)
ldahist(data = CN2.lda.values$x[,4], g=expr2_df_cent_mva$Patients)
```
Scatterplots of the Discriminant Functions
We can obtain a scatterplot of the best two discriminant functions, with the data points labelled by cultivar, by typing:
LD1 + LD2 = ~76.8% separation WITHOUT vDNA or vRNA!
```{r}
plot(CN2.lda.values$x[,1],CN2.lda.values$x[,2]) # make a scatterplot
text(CN2.lda.values$x[,1],CN2.lda.values$x[,2],expr2_df_cent_mva$Patients,cex=0.7,pos=4,col="red") # add labels

```
We can separate out the infected (1, 2, 5, 6) vs uninfected animals (3, 4)!!
## Prettier LDA plot in ggplot
## NOTE WE FLIP LD1 
```{r}
lda_df = data.frame(LD1 = CN2.lda.values$x[,1], LD2 = CN2.lda.values$x[,2], Animals = as.factor(expr2_df_cent_mva$Patients), Infection = expr2_df_cent_mva$Groups)
lda_df$Infection[lda_df$Infection == 0] = "Uninfected Animal"
lda_df$Infection[lda_df$Infection == 1] = "Infected Animal"
lda_df$Infection = factor(lda_df$Infection, levels = c("Infected Animal", "Uninfected Animal"))
lda_df$Animals = factor(lda_df$Animals, levels = c(1,2,5,6,3,4))
## NOTE WE ARE FLIPPING THE LD1
lda_df$LD1 = lda_df$LD1 * -1

library(ggpubr)

# By animal. NOTE Animal 6 is actually acutely infected!
plot1 <- ggplot(lda_df, aes(x = LD1, y = LD2, color = Animals)) + 
  geom_point() + theme_bw() + ggtitle("Linear Discriminant Analysis")

dens1 <- ggplot(lda_df, aes(x = LD1, fill = Animals)) + 
  geom_density(alpha = 0.4) + 
  theme_void() + 
  theme(legend.position = "none")

dens2 <- ggplot(lda_df, aes(x = LD2, fill = Animals)) + 
  geom_density(alpha = 0.4) + 
  theme_void() + 
  theme(legend.position = "none") + 
  coord_flip()

dens1 + plot_spacer() + plot1 + dens2 + 
  plot_layout(ncol = 2, nrow = 2, widths = c(4, 1), heights = c(1, 4))
# ggsave("PaperPlots/LDAplot_ByAnimal.svg")


## By SIV infection 
plot1 <- ggplot(lda_df, aes(x = LD1, y = LD2, color = Infection)) + 
  geom_point() + theme_bw() + ggtitle("Linear Discriminant Analysis")

dens1 <- ggplot(lda_df, aes(x = LD1, fill = Infection)) + 
  geom_density(alpha = 0.4) + 
  theme_void() + 
  theme(legend.position = "none")

dens2 <- ggplot(lda_df, aes(x = LD2, fill = Infection)) + 
  geom_density(alpha = 0.4) + 
  theme_void() + 
  theme(legend.position = "none") + 
  coord_flip()

dens1 + plot_spacer() + plot1 + dens2 + 
  plot_layout(ncol = 2, nrow = 2, widths = c(4, 1), heights = c(1, 4))
# ggsave("PaperPlots/LDAplot_ByInfection.svg")


```

1. Find what determines the LD1 LD2 loadings
Loadings are stored under: CN2.lda$scaling
Plot a ranked plot for each scaling from positive to negative
```{r}
# Try for first LD NOTE * -1 to flip the axis
toplot = as.data.frame(CN2.lda$scaling[,1])*-1
colnames(toplot) = "LD1"
toplot$CN2 = rownames(toplot)
toplot$direction = factor(sign(toplot$LD1), levels = c(-1, 1))
# Order df3 by frequency
# toplot$absval = abs(toplot$LD1)
toplot$CN2 = factor(toplot$CN2 , levels = toplot$CN2[order((toplot$LD1), decreasing = T)])


ggplot(toplot, aes(x = CN2, y = LD1, fill = direction)) + geom_bar(stat = "identity", color = "black") + labs(x = "Variables", y = "Linear Discriminant Loading 1",title = "LD1 Rank Plot") + theme_bw()  + theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) + scale_fill_brewer(palette="Dark2", labels = c("Negative", "Positive"), name = "Direction")

# ggsave("PaperPlots/LDA1_FeatureRankPlot.svg")

```
```{r}
# Try for second LD
toplot = as.data.frame(CN2.lda$scaling[,2])
colnames(toplot) = "LD2"
toplot$CN2 = rownames(toplot)
toplot$direction = as.factor(sign(toplot$LD2))
# Order df3 by frequency
toplot$absval = abs(toplot$LD2)
toplot$CN2 = factor(toplot$CN2 , levels = toplot$CN2[order((toplot$LD2), decreasing = T)])


ggplot(toplot, aes(x = CN2, y = LD2, fill = direction)) + geom_bar(stat = "identity", color = "black") + labs(x = "Variables", y = "Linear Discriminant Loading 1",title = "LD2 Rank Plot") + theme_bw()  + theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) + scale_fill_brewer(palette="Dark2", labels = c("Negative", "Positive"), name = "Direction")

# ggsave("PaperPlots/LDA2_FeatureRankPlot.svg")

```

# Try LDA on marker and CN1
```{r, fig.width=5, fig.height=5}
require(MASS)
# Includes markers, CN1 counts and CN2
expr2_df_cent_mva = expr2_df_cent[,c(4,5, 67, 68,66,51, 12, 14:43, 52:65, 70:100)]
# expr2_df_cent_mva
# # Summarize mean per celltype for Marker
# expr2_df_cent_mva = expr2_df_cent_mva %>% group_by(Groups, Patients, cell_type_for_CN) %>%
#   summarise(across(Vimentin:CD45_20_CN2, mean))

# Summarize mean per CN for CN2/2
expr2_df_cent_mva = expr2_df_cent_mva %>% group_by(Groups, Patients, neighborhood20) %>%
  summarise(across(Vimentin:CD45_20_CN2, mean))


# Remove vDNA and vRNA columns
standardisedconcentrations <- as.data.frame(scale(expr2_df_cent_mva[,c(4:12,14:31, 33:57, 59:76, 78:79)]))
sapply(standardisedconcentrations,mean)
sapply(standardisedconcentrations,sd)

# LDA on markers
# marker.lda <- MASS::lda(standardisedconcentrations[,c(1:29)], grouping = expr2_df_cent_mva$Patients)
# marker.lda.values <- predict(marker.lda, standardisedconcentrations[,c(1:29)])
# LDA on CN1s
marker.lda <- MASS::lda(standardisedconcentrations[,c(30:43)], grouping = expr2_df_cent_mva$Patients)
marker.lda.values <- predict(marker.lda, standardisedconcentrations[,c(30:43)])


# Proportion of trace is how much each % separation achieved by each LD
marker.lda
ldahist(data = marker.lda.values$x[,1], g=expr2_df_cent_mva$Patients)
ldahist(data = marker.lda.values$x[,2], g=expr2_df_cent_mva$Patients)
ldahist(data = marker.lda.values$x[,3], g=expr2_df_cent_mva$Patients)
ldahist(data = marker.lda.values$x[,4], g=expr2_df_cent_mva$Patients)
plot(marker.lda.values$x[,1],marker.lda.values$x[,2]) # make a scatterplot
text(marker.lda.values$x[,1],marker.lda.values$x[,2],expr2_df_cent_mva$Patients,cex=0.7,pos=4,col="red") # add labels

# CEll Type for Markers
# lda_df = data.frame(LD1 = marker.lda.values$x[,1], LD2 = marker.lda.values$x[,2], Animals = as.factor(expr2_df_cent_mva$Patients), Infection = expr2_df_cent_mva$Groups, CellType = as.factor(expr2_df_cent_mva$cell_type_for_CN))

lda_df = data.frame(LD1 = marker.lda.values$x[,1], LD2 = marker.lda.values$x[,2], Animals = as.factor(expr2_df_cent_mva$Patients), Infection = expr2_df_cent_mva$Groups, CN = as.factor(expr2_df_cent_mva$neighborhood20))

lda_df$Infection[lda_df$Infection == 0] = "Uninfected Animal"
lda_df$Infection[lda_df$Infection == 1] = "Infected Animal"
lda_df$Infection = factor(lda_df$Infection, levels = c("Infected Animal", "Uninfected Animal"))
lda_df$Animals = factor(lda_df$Animals, levels = c(1,2,5,6,3,4))
# ## NOTE WE ARE FLIPPING THE LD1
lda_df$LD1 = lda_df$LD1 * -1

library(ggpubr)

# By animal. NOTE Animal 6 is actually acutely infected!
plot1 <- ggplot(lda_df, aes(x = LD1, y = LD2, color = Animals)) + 
  geom_point() + theme_bw() + ggtitle("Linear Discriminant Analysis by CN per Animal only")

dens1 <- ggplot(lda_df, aes(x = LD1, fill = Animals)) + 
  geom_density(alpha = 0.4) + 
  theme_void() + 
  theme(legend.position = "none")

dens2 <- ggplot(lda_df, aes(x = LD2, fill = Animals)) + 
  geom_density(alpha = 0.4) + 
  theme_void() + 
  theme(legend.position = "none") + 
  coord_flip()

dens1 + plot_spacer() + plot1 + dens2 + 
  plot_layout(ncol = 2, nrow = 2, widths = c(4, 1), heights = c(1, 4))
ggsave("PaperPlots/LDAplot_ByAnimal_CN1Only.svg")


## By SIV infection 
plot1 <- ggplot(lda_df, aes(x = LD1, y = LD2, color = Infection)) + 
  geom_point() + theme_bw() + ggtitle("Linear Discriminant Analysis by CN per Infection only")

dens1 <- ggplot(lda_df, aes(x = LD1, fill = Infection)) + 
  geom_density(alpha = 0.4) + 
  theme_void() + 
  theme(legend.position = "none")

dens2 <- ggplot(lda_df, aes(x = LD2, fill = Infection)) + 
  geom_density(alpha = 0.4) + 
  theme_void() + 
  theme(legend.position = "none") + 
  coord_flip()

dens1 + plot_spacer() + plot1 + dens2 + 
  plot_layout(ncol = 2, nrow = 2, widths = c(4, 1), heights = c(1, 4))

ggsave("PaperPlots/LDAplot_ByInfection_CN1Only.svg")

```

## Way forward Random Forest:
Find stratifying features between Latent and Lytic
Use a random forest
```{r}
trainingdata = infected_cells_df[infected_cells_df$latency_status %in% c("Latent", "Active"),]
trainingdata$latency_status = factor(trainingdata$latency_status, levels = c("Latent", "Active"))
# Use only cell markers
trainingdata_markers = trainingdata[,c(12, 14:21, 23:40, 42:43, 69)]
```

## Try Han's function
Input dataframe is matrix with rows for each patient/donor. Columns are features. First column is the outcome
```{r}
# Rework trainingdata_CN2s a little
# latency_status becomes Shedding (factor with levels 0 and 1)
trainingdata_CN2s = trainingdata[,c(69, 70:78, 80:97,99:100)]
colnames(trainingdata_CN2s)[colnames(trainingdata_CN2s) %in% "latency_status"] = "Shedding"
trainingdata_CN2s$Shedding = as.character(trainingdata_CN2s$Shedding)
trainingdata_CN2s$Shedding[trainingdata_CN2s$Shedding %in% "Latent"] = 0
trainingdata_CN2s$Shedding[trainingdata_CN2s$Shedding %in% "Active"] = 1
trainingdata_CN2s$Shedding = factor(trainingdata_CN2s$Shedding, levels = c(0, 1))

rf_out = iterate_random_forest(df_input = trainingdata_CN2s, tuneLength = 50)
```

```{r}
rf_out$pval_plot
rf_out$model_prediction_boxplot
rf_out$roc_plot
```
Write a loop to go through markers, CNs and CN2s
TRY: Adding cell types

```{r}
# No NFkB
ran_f_types_noNF = list(Markers = c(69, 12, 14:16, 18:21, 23:40, 42:43),
                   CNs = c(69, 52:66),
                   CN2s = c(69, 70:73, 75:78, 80:97,99:100), # Originally used 69, 70:100 which included vDNA and vRNA so fail, of course it predicts reactivation...
                   Markers_CN2s = c(69, 12, 14:16, 18:21, 23:40, 42:43, 70:73, 75:78, 80:97,99:100),
                   Markers_CN1s = c(69, 12, 14:16, 18:21, 23:40, 42:43,52:66),
                   CN1s_CN2s = c(69, 52:66, 70:73, 75:78, 80:97,99:100),
                   CN_only = c(69, 66))
                   

rf_out_list = mclapply(ran_f_types_noNF, function(rf){
  trainingdata_sub = trainingdata[,rf]
  print(colnames(trainingdata_sub))
  colnames(trainingdata_sub)[colnames(trainingdata_sub) %in% "latency_status"] = "Shedding"
  trainingdata_sub$Shedding = as.character(trainingdata_sub$Shedding)
  trainingdata_sub$Shedding[trainingdata_sub$Shedding %in% "Latent"] = 0
  trainingdata_sub$Shedding[trainingdata_sub$Shedding %in% "Active"] = 1
  trainingdata_sub$Shedding = factor(trainingdata_sub$Shedding, levels = c(0, 1))
  rf_out = iterate_random_forest(df_input = trainingdata_sub, tuneLength = 20, ntree = 2000)  
},mc.cores = 6)

lapply(rf_out_list, function(rf){
  rf$roc_plot
})
```
Plotting all the AUCs together
```{r}

df_all_AUC = do.call(rbind,lapply(names(rf_out_list), function(rf){
  df = rf_out_list[[rf]][["prediction_performance"]]
  df$Model = rf
  return(df)
}))

AUC_values = unlist(lapply(names(rf_out_list), function(rf){
  paste0(rf, ": ", round(rf_out_list[[rf]][["prediction_performance_auc"]],5))
}))

df_all_AUC$Model = factor(df_all_AUC$Model, levels = names(ran_f_types))

p = ggplot(df_all_AUC, aes(x = FPR, y = TPR, group = Model))
p + geom_line(aes(color = Model), size = 0.5) + theme_bw() + 
    geom_abline(slope = 1,
              intercept = 0,
              linetype = "dashed",
              color = "red",
              alpha = 0.5,
              size = 0.5) + ggtitle(paste(AUC_values, collapse = " ")) + scale_color_discrete(labels = AUC_values)
  
ggsave("PaperPlots/ROC_AUC_7Models_ntree2000_novRNAhi_noNFkB.svg")


# 3 models

df_all_AUC = do.call(rbind,lapply(names(rf_out_list)[c(1,3,7)], function(rf){
  df = rf_out_list[[rf]][["prediction_performance"]]
  df$Model = rf
  return(df)
}))

AUC_values = unlist(lapply(names(rf_out_list)[c(1,3,7)], function(rf){
  paste0(rf, ": ", round(rf_out_list[[rf]][["prediction_performance_auc"]],5))
}))

df_all_AUC$Model = factor(df_all_AUC$Model, levels = names(ran_f_types))

p = ggplot(df_all_AUC, aes(x = FPR, y = TPR, group = Model))
p + geom_line(aes(color = Model), size = 0.5) + theme_bw() + 
    geom_abline(slope = 1,
              intercept = 0,
              linetype = "dashed",
              color = "red",
              alpha = 0.5,
              size = 0.5) + ggtitle(paste(AUC_values, collapse = " ")) + scale_color_discrete(labels = AUC_values)
  
ggsave("PaperPlots/ROC_AUC_3Models_ntree2000_novRNAhi_noNFkB.svg", width = 8,height = 5)

```